%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Backend Developer, Project Management, Software Architect \& DevOps} % Job title
    {xwave Group Deutchland GmbH} % Organization
    {Frankfurt am Main, Germany} % Location
    {Dec. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Everything that matters.}
        \item {Staff Training: how to define a REST based microservice with NodeJS and Fastify. I have given interactive lesson to my collegues.}
        \item {Software Architect. Implementation of mediator pattern for distribuite and decouple microservice. Advanced mediator with internal scheduler defined by policy parameters. Backup/report on mysql db, command \& job spawn via RabbitMQ.}
        \item {Project Management. Install and use Redmine on premise, with module for kanban/scrum. Setup some ritual (weekly meeting). I am not a scrum expert, it is not my skill, but I did.}
        \item {System admin \& DevOps. Setup GOGS (and then GITEA), and Jenkins for building and run integration tests on microservices.}
        \item {Software Architect. Configurable gateway images, talking with internal microservice and implementing JWT auth for the outer world. Multi-step and JSON request aware.}
        \item {System admin \& Backend Dev. Setup a Docker Swarm with 3 nodes (2018). First port of backend script to Docker Swarm. Microservice talking REST.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer - Consultant} % Job title
    {xwave Group Deutchland GmbH} % Organization
    {Frankfurt am Main, Germany} % Location
    {Dec. 2014 - Dec. 2017} % Date(s)
    {
      \begin{cvitems}
        \item {Desktop App. Electron + React that use REST API to get customer's data to print and change status.}
        \item {Backend service. Stand-alone NodeJS based service, was the begin to my backend journey in xwave.}
        \item {Front end. jQuery \& jqGrid Javascript library for presentation of data.}
        \item {PHP. Used as apache module for suppling data to the frontend. Optimization of session data preparation, check for permission, profile \& optimize response time.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Linguistic Studio} % Organization
    {Macerata, Italy} % Location
    {Sep. 2013 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {NodeJS. API for ecommerce ebay integration \& central synchronization by a service.}
        \item {Javascript. AngularJS (1.0) frontend for ecommerce synchronization service.}
        \item {Drupal. Ecommerce integration for ebaysync service: hook on purchase and periodical synchronization of stock levels.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {WMR s.r.l. Studio Cappello} % Organization
    {Saonara, PD, Italy} % Location
    {Sep. 2013 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Drupal \& Web Development. Website fix and optimization for a number of customers (ecommerce).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Linguistic Studio} % Organization
    {Macerata, Italy} % Location
    {Oct. 2010 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Drupal. Bugfix and optimization for ecommerce and other website.}
        \item {Drupal module development for third party (XML) service integration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer}
    {IM Evolution}
    {Taviano, Lecce, Italy}
    {Jul. 2005 - Dec. 2014} % Date(s)
    {
      \begin{cvitems}
        {PHP and HTML. A number of web technology integration, like RSS, indexing for spiders, HTML formatting for SEO optimization, and so on.}
        {jQuery. Administration panel for content edit and creation.}
        {Perl, MySQL \& HTML. Content generator scripts from database MySQL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer}
    {IRISNet Solution}
    {Pisa, Italy}
    {Oct. 2010 - Dec. 2012} % Date(s)
    {
      \begin{cvitems}
        {Most of the works done for xwave GmbH.}
        {PHP \& Javascript. Development and bugfix of web applications.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer}
    {Confestetica}
    {Rimini, Italy}
    {May 2009 - Jun. 2010} % Date(s)
    {
      \begin{cvitems}
        {PHP + jQuery + AJAX. Community site: confestetica.it. I implemented a GUI similar to facebook, using AJAX to get preview and post without reloading.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Smartphone Developer}
    {Portel s.r.l.}
    {Milano, Italy}
    {Feb. 2007 - Sep. 2007} % Date(s)
    {
      \begin{cvitems}
        {Symbian OS 8.1 to 9.1. Porting of an existing Mobile App from Symbian OS 2^nd edition (8.1) App to Symbian OS 3^rd Edition (9.1).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer}
    {Wind S.p.a.}
    {Pisa, Italy}
    {May 2005 - Jul. 2005} % Date(s)
    {
      \begin{cvitems}
        {PHP Development. digiland.libero.it community site, restyling of css.}
        {XSL/XSLT transformation for generating contents from XML source.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer}
    {Dr.Net coop}
    {Macerata, Italy}
    {May 2004 - Jun. 2004} % Date(s)
    {
      \begin{cvitems}
        {PHP. Extension to PHP Nuke framework.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Symbian OS Developer}
    {A-Tono S.r.l.}
    {Milano, Italy}
    {Jun. 2003 - Jan. 2004} % Date(s)
    {
      \begin{cvitems}
        {Symbian OS 6.1. Http/1.1 library handcrafted for the project.}
        {Symbian OS 6.1. Interface scrolling and selecting data to download.}
        {Planned the use of SMS interface for payment system (reverse billing).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Development}
    {Myself}
    {Italy}
    {2002 - 2005} % Date(s)
    {
      \begin{cvitems}
        {Started a number of project, including J2ME client, Computo Metrico (to make estimation of cost in construction) with XCode and Objective C.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer} % Job title
    {Santoni Fulvio Costruzioni, S.n.c} % Organization
    {Camerino, MC, Italy} % Location
    {Feb. 2003 - Mar 2003} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Java Applet for computing forces of reticular bridge. Interactive input (with instrument palette), calculation using Gauss/Jordan with pivot for stability, and with singularity detection.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Design && Develop} % Job title
    {Noze S.r.l.} % Organization
    {Cascina, PI, Italy} % Location
    {Mar. 2002 - Oct 2002} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Monitoring, collecting of sensible data system (for hotel presense): a MS win client, a number of collecting server, one monitoring server. Definition and implementation of network protocol (HTTP/1.1 based, over PSTN line). Design and implementation of two daemons: a collector service, for controlling incoming pppd connection, and monitoring
service, for statistics. Using PostgreSQL, and PHP for web interface.}
        \item {Parse a binary log. Program that generate report from a binary log file genarated from a gsm/gprm logger (similar to radius). LL(1) Parser, POSIX pthread, and autoconf/automake.}
        \item {Analysis on Global FS and dfs implementation of an app. (not benchmark, just theoretical) }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}